\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-13 trunk/europa-basics.tex
updates

\paragraph \textit{Scheduling}: In the Resource Constrained Project
Scheduling Problem (RCPSP) \comment{citations needed}, a project
consisting of a set of activities must be scheduled in a way that
satisfies minimum and/or maximum temporal separation constraints. The
activity schedule must also respect fixed limits on the availability of
resources required to perform each activity. In addition to satisfying
temporal and resource constraints, it is common for the user to want to
minimize makespan so that the entire project is finished as early as
possible. Fig. \ref{fig:rcpsp-1} shows an example of a a solution
provided by \eu for an RCPSP instance with 10 activities, 5 resources
and 30 temporal constraints.

>>>>

\paragraph \textit{Scheduling}: In the Resource Constrained Project
Scheduling Problem (RCPSP) \cite{Bruckera99}, a project consisting of
a set of activities must be scheduled in a way that satisfies minimum
and/or maximum temporal separation constraints. The activity schedule
must also respect fixed limits on the availability of resources
required to perform each activity. In addition to satisfying temporal
and resource constraints, it is common for the user to want to
minimize makespan so that the entire project is finished as early as
possible. Fig. \ref{fig:rcpsp-1} shows an example of a a solution
provided by \eu for an RCPSP instance with 10 activities, 5 resources
and 30 temporal constraints.
